%-----------------------------------------------------------------------------%

% Letter class
\documentclass[a4paper, 10pt]{letter}

% Name of sender
\name{Lewis Marshall}

% Signature of sender
\signature{Lewis Marshall}

% Address of sender
\address
{
    Lewis Marshall,\\
    5210 Fiore Terrace, San Diego, CA
    92122
}

%-----------------------------------------------------------------------------%

\begin{document}

% Name and address of receiver
\begin{letter}
{
    Sept 19, 2024\\
    General Atomics\\
    Job ID 45343BR
}

% Opening statement
\opening{Dear hiring manager,}

% Letter body
I'm writing you to apply for the job listed as "Senior Manager, Science and Technology Products System Engineering Directorate".  I was referred to your website by a collegue
because of the impressive bredth of your work. I hope you'll consider
me for the role because of my strong experience as a systems engineer and an engineering manager.

As a systems engineer, I've always adapted to the needs of the project. At the early phase of my career, I was responsible for making big-picture decisions about
the architecutre of our system. I worked with contractors to manufacture our instrument, and wrote the manufacturing tests to ensure stable system performance. I worked closely with 
my team to develop new products, and always pushed them to develop their skills on the job. And when problems came up, I went wherever
the data pointed. I ended up troubleshooting elements as complex as our fluid dynamics patterns and as simple as our choices of o-ring
and screw. We were proud of both the performance and the reliability of our product.

On a personal note, I'm happy that your posting emphasizes the need for this manager to be an ethical role model and to uphold a high standard of quality 
for the team. Before I was ever an engineer, I grew up in a small midwestern town, and my gradfather taught me an important lesson. "If you're not going to
do it right, don't do it at all." I bring that value with me to my work. To me, that means creating a robust testing plan, a sound theoretical understanding, and a system for 
tracking performance over time. Most importantly, I never want to sweep a problem under the rug. 

Please see my resume, which details my experience and qualifications for the position. Please don't hesitate to contact me if you have any questions, and I hope we 
get a chance to discuss my fit for the role in person. 

% Closing statement
\closing{Thank you for your time and consideration,}

\end{letter}
\end{document}
%-----------------------------------------------------------------------------%