%-----------------------------------------------------------------------------%

% Letter class
\documentclass[a4paper, 10pt]{letter}

% Name of sender
\name{Lewis Marshall}

% Signature of sender
\signature{Lewis Marshall}

% Address of sender
\address
{
    Lewis Marshall,\\
    5210 Fiore Terrace, San Diego, CA
    92122
}

%-----------------------------------------------------------------------------%

\begin{document}

% Name and address of receiver
\begin{letter}
{
    October 9, 2024\\
    General Atomics\\
    Job ID 45343BR
}

% Opening statement
\opening{Dear hiring manager,}

% Letter body
I'm writing you to apply for the job listed as "Engineer Instrumentation and Control".  I was referred to you by a collegue because of my interest in fusion
research programs. I hope you'll consider me for the role because of my strong experience as a multidisciplinary engineer.

My background in the startup environment has allowed me to develop the type of multidisciplinary skills that you're seeking in this role. 
I've had the opportunity to be the designer for mechanical systems, electrical systems, and software systems for the last decade. 
I've also worked with internal team members and external contractors to manufacture our instrument, and wrote the manufacturing tests to 
ensure stable system performance. Through it all, the ability to write fluent python has been invaluable, both to process always-increasing
volumes of data, and to design data collection and control algorithms. 

While this role would be a reduction from my title in the biotech industry, I have a keen interest in fusion technology. Our energy needs are \textbf{the}
critical problem in the $21^{st}$ century, and the potential for fusion to supply clean, plentifuly energy is a great hope for humanity's future. I
view this as an entry position to pursue a career in fusion technology. 

Please see my resume, which details my experience and qualifications for the position. Please don't hesitate to contact me if you have any questions, and I hope we 
get a chance to discuss my fit for the role in person. 

% Closing statement
\closing{Thank you for your time and consideration,}

\end{letter}
\end{document}
%-----------------------------------------------------------------------------%