%-----------------------------------------------------------------------------%

% Letter class
\documentclass[a4paper, 10pt]{letter}

% Name of sender
\name{Lewis Marshall}

% Signature of sender
\signature{Lewis Marshall}

% Address of sender
\address
{
    Lewis Marshall,\\
    5210 Fiore Terrace, San Diego, CA
    92122
}

%-----------------------------------------------------------------------------%

\begin{document}

% Name and address of receiver
\begin{letter}
{
    Sept 24, 2024\\
    Roche\\
}

% Opening statement
\opening{Dear hiring manager,}

% Letter body
I'm writing you to apply for the position as Senior Director, Mechanical Engineering. While I initially passed over this role because of my background in chemical engineering, I think that the responsibilities you list for the role are a great fit for my experience. 

I've spent my career as a system engineer for the automated manipulation of nucleic acids. This includes over 10 years of engineering over 3 systems, with 7 years of management experience. I've always led highly multidisciplinary teams, with biologists, and engineers specializing in mechanical, electrical, biomedical, and softwear systems. 

On each system that I've worked on, my focus has been reliability and quality. For the Ionic system, we achieved quality through rigorous testing (using ANSI standard methods) and manufacturing controls, eventually achieving a device robustness of over 98 percent.

Over this time, my favorite experiences were in the fast-paced startup environment.  I led teams launching our systems most successful products for nucleic acid purification. I developed an intimate knowledge of our system, down to individual board components. I ultimately wrote the business logic for our automation, and that logic is still in use today. 

Please see my resume, which details my experience and qualifications for the position. Please don't hesitate to contact me if you have any questions, and I hope we 
get a chance to discuss my fit for the role in person. 

% Closing statement
\closing{Thank you for your time and consideration,}

\end{letter}
\end{document}
%-----------------------------------------------------------------------------%