%-----------------------------------------------------------------------------%

% Letter class
\documentclass[a4paper, 10pt]{letter}

% Name of sender
\name{Lewis Marshall}

% Signature of sender
\signature{Lewis Marshall}

% Address of sender
\address
{
    Lewis Marshall,\\
    5210 Fiore Terrace, San Diego, CA
    92122
}

%-----------------------------------------------------------------------------%

\begin{document}

% Name and address of receiver
\begin{letter}
{
    October 21, 2024\\
    Quantum SI\\
}

% Opening statement
\opening{Dear Pat,}

% Letter body
I'm writing you to apply for the job of Senior Principal Systems engineer at Quantum SI. I hope you'll consider me for the role 
based on my previous experience as the system architect for the Purigen Ionic. In that role, I worked on every part of the system -- 
hardware, software, electrical boards, and biological designs. My belief
is that a system engineer should and must be aware of all these areas to manage and produce a robust system.

While you met me in the context of a mature Ionic system, that was a result of years of work by me and the rest of the team
to develop each element in parallel. In the early phases, this consisted 
of design specification and simplification. I designed the microfluidic system and specified the interfaces to our hardware engineering
contractor to ensure correct matches through generations of products. I specified the requirements for our high voltage system to 
minimize hardware complexity while maximizing flexibility. I managed Sean Arin as he took over the hardware engineering for the pressure
subsystem, when our engineering contractor that couldn't produce the desired precision. 

Later, more of the work focused on identifying and fixing issues to ensure
a robust platform. In this phase I identified evaporation as a key issue in platform robustness, and helped implement and test an air-flow blocking solution
to solve the problem. I took on DFM of the manifold to improve manufacturing yield, and personally identified errors in the screw selection 
and o-ring design that were resulting in leaks. I led the rest of the hardware engineering team as we fixed customer instruments. And I 
worked with Paramit to ensure we received instruments even during the most challenging years of the pandemic.

Beyond my technical experience, I've worked to lead my teams with transparency and urgency. When Purigen matured, we worked under a formal PDP process. 
I kept Gantt charts that identified key milestones and points of risks, and updated them regularly. I always put myself at the point of the most critical actions, 
whether that was helping find electronic components or analyzing data to find platform issues. And through it all, I had a great time, because platform engineering
is truly something I love to do. 

Please see my resume, which details my experience and qualifications for the position. Please don't hesitate to contact me if you have any questions. 
I look forward to discussing further with you. 

% Closing statement
\closing{Thank you for your time and consideration,}

\end{letter}
\end{document}
%-----------------------------------------------------------------------------%