\documentclass{res}
% \usepackage[compact]{titlesec}
% \titlespacing{\section}{0pt}{2ex}{1ex}
% \titlespacing{\subsection}{0pt}{1ex}{0ex}
% \titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage[T1]{fontenc}
\usepackage{kpfonts,baskervald}
% \setlength{\textheight}{8.5in} % increase text height to fit on 1-page

\begin{document}

\name{Lewis A. Marshall, Ph.D.}%\\[12pt]}     % the \\[12pt] adds a blank

\address{5210 Fiore Terrace L205 \\ San Diego, CA 92122 \\ (650) 391-8463}

\address{Citizenship: United States \\ \\ lewis.a.marshall@gmail.com}

\begin{resume}

\section{AN R\&D LEADER}
  \begin{itemize}
    \item Delivers complex integrated systems.
    \item Specialist in designing microfluidic devices and electrophoretic processes.
    \item Experience in biology, chemistry, hardware, software, and data analysis.
    \item Extensive experience working with contract engineering and manufacturing partners.
    \item Motivates technical teams to solve challenging problems with engagement and focus.
    \item Responsive to customer needs and focused on long-term organizational success.
  \end{itemize}



\section{EXPERIENCE}
\vspace{-0.1in}


   \subsection{Bionano, San Diego CA}
    \vspace{-0.1in}
   \subsubsection{Director, Platform Technology \> 2023-Present}
  %  \vspace{-0.1in}
    \begin{itemize}
     \item Relocated to Bionano Headquarters after acquisition of Purigen Biosystems to aid critical technolgy transfer.
     \item Leader of the Systems Engineering Team.
     \item Reponsible for sustaining systems engineering for both Optical Genome Mapping (OGM) and the Ionic Purification systems. 
     \item Developed signal processing to diagnose a critical, customer-facing problems on the OGM platform
     \item Proof of concept for a method to scale up OGM sample preparation througput.  
     \item Drove multiple platform robustness issues to root cause to improve customer experience
    \end{itemize}


   \subsection{Purigen Biosystems, Pleasanton CA}
    \vspace{-0.1in}

    \subsubsection{Vice President, R\&D \> 2021-2022}
      \vspace{-0.1in}
      % Overall leader of the R\&D efforts at Purigen, including product teams, as well as
      % continuing platform and microfluidic development.
      R\&D leader reporting to the CSO. Responsibility spanning product development, instrument
      manufacturing, software development, and microfluidic design.
      \vspace{0.1in}
       \begin{itemize}
        \item Managed a 15-member R\&D team and \$5M annual budget through the COVID-19 pandemic.
        \item Expanded Purigen's oncology portfolio by launching a Tissue to DNA. 
        \item Worked through supply chain issues to deliver electronic part kits for a critical instrument build.
        \item Created a sustainable system for customer support to solve customer problems.
        \item Implemented ANSI-standard testing for critical parts to improve quality.
        \item Chose key design features for a High Molecular Weight DNA extraction consumable.
        \item Conducted a Design For Manufacturing review of the Ionic instrument, streamlining future builds.
        % \item Developed hardware-simulation
        \item Managed external software contractors to improve instrument stability and launch new products.
       \end{itemize}

      \vspace{-0.2in}
    \subsubsection{Director/Senior Manager, Fluidics \> 2018-2021}
      \vspace{-0.2in}
      Leader of a product team creating new products for the Purigen Ionic platform,
      including development of lysis protocols, separation chemistry, and downstream application data.
      \vspace{0.1in}
       \begin{itemize}
        \item Created two products, including the best in class FFPE to DNA sample prep solution.
        \item Combined separate biological and microfluidic groups into one product-first group.
        \item Identified platform failure modes using signal analysis and image velocimetry.
        \item Wrote a bioinformatics pipeline to identify Purigen's advantage in sequencing uniformity.
        \item Encouraged continuing technical education by creating a monthly time to review key journal articles. 
       \end{itemize}

% \pagebreak

      \vspace{-0.2in}
    \subsubsection{Lead Engineer \> 2013-2018}
      \vspace{-0.2in}
      Overall system architect responsible for translating theory and experience with isotachophoresis
      into an automated, customer-ready system.
      \vspace{0.1in}
      \begin{itemize}
        \item Designed the microfluidic device used to launch Purigen's first product.
        \item Designed the interfaces between the Purigen Ionic instrument and consumable to fit future roadmap.
        \item Wrote and maintained the business logic software for the Purigen Ionic instrument.
        \item Worked with engineering contractors to implement instrument design and firmware.
        \item Created and maintained the self-test suite for the Purigen Ionic to simplify manufacturing process.
        \item Wrote automated reporting infrastructure to characterize individual instrument runs.
        \item Wrote data aggregation software to compile metrics from thousands of individual samples.
      \end{itemize}

   % \begin{tabbing}
   % Vice President, R\&D  \> July~2021-Present \\
   % Director of Fluidics \> July~2019-July~2021 \\
   % Senior Manager, Fluidics \> Jan~2018-July~2019\\
   % Lead Engineer        \>July~2013-Jan~2018 \\
   % \end{tabbing}\vspace{-20pt}


\section{EDUCATION}
    \begin{itemize}
  		\item{Ph.D., Chemical Engineering}\\
		  Stanford University, 2008--2013 \\
  		Advisor: Juan G. Santiago\\
      Thesis: Designing Automated Systems For Sample Preparation Of Nucleic Acids Using Isotachophoresis
  	  \item{B.S., Chemical Engineering}\\
		  University of Minnesota, 2004--2008 \\
      Research Advisor: Wei-Shou Hu
    \end{itemize}

 \section{SELECTED PUBLICATIONS}
  \begin{itemize}
  \item Marshall, L.A.; Rogacs, A.; Meinhart, C.D.; Santiago, J.G. An injection molded microchip for nucleic acid purification from 25 microliter samples using isotachophoresis. Journal of Chromatography A \textbf{2014}, 1331, 139-142.
  \item Rogacs, A.; Marshall, L.A.; Santiago, J.C. Purification of nucleic acids using isotachophoresis. Journal of Chromatography A \textbf{2014}, 1335, 105–120.
\end{itemize}

 \section{SELECTED PATENTS}
   \begin{itemize}
    \item Capillary barriers for staged loading of microfluidic devices (2018), US10787660B2. US.  
    \item Systems, devices, and methods for isotachophoresis (2018), US11041150B2. US.
    \item Isotachophoresis for purification of nucleic acids, (2018), US201662288930P. US. 
   \end{itemize}


 \section{OPEN SOURCE}
   \begin{itemize}
     \item \textbf{Ionize} github.com/lewisamarshall/ionize\\
   An object oriented Python library for calculating the properties of
   aqueous solutions, including corrections for temperature, ionic strength, and ion-ion interactions.
 \end{itemize}


 % \section{SKILLS}
 %   \begin{itemize}
 %     \item \textbf{Project Management}	Lead projects transparently to schedule while updating with the latest technical information.
 %     \item \textbf{Hiring}	Experienced leading hiring committees using transparent, modern hiring practices.
 %     \item \textbf{Programming}	Fluent in Python. Experienced managing contractors and in-house programmers to build a complete system.
 %     \item \textbf{Version Control} Experienced creating and managing Github repositories.
 %   \end{itemize}


%  \section{OTHER INTERESTS}
%    \begin{itemize}
%      \item \textbf{Woodworking}	I use hand tools and traditional techniques to make American vernacular furniture.
%      \item \textbf{Photography}	My use of scientific imaging led me to explore artistic photography.
%    \end{itemize}


\end{resume}
\end{document}
