\documentclass{res}
% \usepackage[compact]{titlesec}
% \titlespacing{\section}{0pt}{2ex}{1ex}
% \titlespacing{\subsection}{0pt}{1ex}{0ex}
% \titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage[T1]{fontenc}
\usepackage{kpfonts,baskervald}
% \setlength{\textheight}{8.5in} % increase text height to fit on 1-page

\begin{document}

\name{Lewis A. Marshall, Ph.D.}%\\[12pt]}     % the \\[12pt] adds a blank

\address{5210 Fiore Terrace L205 \\ San Diego, CA 92122 \\ (650) 391-8463}

\address{Citizenship: United States \\ \\ lewis.a.marshall@gmail.com}

\begin{resume}

\section{Multidisciplinary Platform Engineer}
  \begin{itemize}
    \item System architect for the Purigen Ionic instrument.
    \item Experience taking ownership of every aspect of a product.
    \item Skilled at combining hardware engineering, software development, and data analysis.
    \item Extensive experience working with contract engineering and manufacturing partners.
    % \item Motivates technical teams to solve challenging problems with engagement and focus.
  \end{itemize}



\vspace{-0.2in}
\section{EXPERIENCE}
\vspace{-0.1in}


   \subsection{Bionano, San Diego CA}
    \vspace{-0.2in}
   \subsubsection{Director, Platform Technology \> 2023-Present}
  %  \vspace{-0.1in}
    \begin{itemize}
     \item Relocated to Bionano Headquarters after acquisition of Purigen for critical technolgy transfer.
     \item Leader of the Systems Engineering Team, reponsible for sustaining systems engineering for both Optical Genome Mapping (OGM) and the Ionic Purification systems. 
     \item Developed signal processing to diagnose a critical, customer-facing problems on the OGM platform
     \item Reviewed high voltage hardware design and firmware to identify root cause of control instability.
     \item Drove multiple platform robustness issues to root cause to improve customer experience
     \item Participated in early builds of next gen instrumentation, provided DFM feedback.
    \end{itemize}


    \vspace{-0.2in}
   \subsection{Purigen Biosystems, Pleasanton CA}
    \vspace{-0.2in}

    \subsubsection{Vice President, R\&D \> 2021-2022}
      \vspace{-0.2in}
      % Overall leader of the R\&D efforts at Purigen, including product teams, as well as
      % continuing platform and microfluidic development.
      R\&D leader reporting to the CSO. Responsibility spanning product development, instrument
      manufacturing, software development, and microfluidic design.
      \vspace{0.1in}
       \begin{itemize}
        \item Managed a 15-member R\&D team and \$5M annual budget through the COVID-19 pandemic.
        \item Managed external contractors for hardware, software, and manufacturing to meet instrument deadlines.
        % \item Expanded Purigen's oncology portfolio by launching a Tissue to DNA. 
        \item Selected alternate electronic parts to mitigate supply chain issues for a critical instrument build.
        % \item Created a sustainable system for customer support to solve customer problems.
        \item Implemented ANSI-standard testing for critical parts to improve quality.
        % \item Chose key design features for a High Molecular Weight DNA extraction consumable.
        \item Conducted a Design For Manufacturing review of the Ionic instrument, streamlining future builds.
        \item Developed hardware-simulation PCBs to simplify component validation at vendor.
        \item Developed data analysis pipelines to aggregate hundreds of instrument runs.
        \item Maintained system business logic in-house to ensure rapid iteration with product teams.
        % \item Developed hardware-simulation
       \end{itemize}

      \vspace{-0.2in}
    \subsubsection{Director/Senior Manager, Fluidics \> 2018-2021}
      \vspace{-0.2in}
      Leader of a product team creating new products for the Purigen Ionic platform,
      including development of software and hardware elements.
      \vspace{0.1in}
       \begin{itemize}
        \item Created two products, including the best in class FFPE to DNA sample prep solution.
        \item Combined separate biological and microfluidic groups into one product-first group.
        \item Improved platform robustness with data driven changes to hardware.
        \item Identified platform failure modes using signal analysis and image velocimetry.
        \item Wrote a bioinformatics pipeline to identify Purigen's advantage in sequencing uniformity.
        \item Encouraged team technical education by creating a monthly time to review key journal articles. 
       \end{itemize}


      \vspace{-0.2in}
    \subsubsection{Lead Engineer \> 2013-2018}
      \vspace{-0.2in}
      Overall system architect responsible for translating theory and experience with isotachophoresis
      into an automated, customer-ready system.
      \vspace{0.1in}
      \begin{itemize}
        \item Designed the microfluidic device used to launch Purigen's first product.
        \item Designed the interfaces between the Purigen Ionic instrument and consumable to fit future roadmap.
        \item Wrote hardware specifications for contract engineers to design hardware and electronic systems.
        \item Collaborated with engineering contractors hands-on to implement and troubleshoot designs.
        \item Wrote and maintained the business logic software for the Purigen Ionic instrument.
        \item Created and maintained the self-test suite for the Purigen Ionic to simplify manufacturing process.
        \item Wrote automated reporting infrastructure to characterize individual instrument runs.
      \end{itemize}

   % \begin{tabbing}
   % Vice President, R\&D  \> July~2021-Present \\
   % Director of Fluidics \> July~2019-July~2021 \\
   % Senior Manager, Fluidics \> Jan~2018-July~2019\\
   % Lead Engineer        \>July~2013-Jan~2018 \\
   % \end{tabbing}\vspace{-20pt}


\section{EDUCATION}
    \begin{itemize}
  		\item{Ph.D., Chemical Engineering}\\
		  Stanford University, 2008--2013 \\
  		Advisor: Juan G. Santiago\\
      Thesis: Designing Automated Systems For Sample Preparation Of Nucleic Acids Using Isotachophoresis
  	  \item{B.S., Chemical Engineering}\\
		  University of Minnesota, 2004--2008 \\
      % Research Advisor: Wei-Shou Hu
    \end{itemize}
      \vspace{-0.2in}

 \section{SELECTED PUBLICATIONS}
  \begin{itemize}
  \item Marshall, L.A.; Rogacs, A.; Meinhart, C.D.; Santiago, J.G. An injection molded microchip for nucleic acid purification from 25 microliter samples using isotachophoresis. Journal of Chromatography A \textbf{2014}, 1331, 139-142.
  \item Rogacs, A.; Marshall, L.A.; Santiago, J.C. Purification of nucleic acids using isotachophoresis. Journal of Chromatography A \textbf{2014}, 1335, 105–120.
\end{itemize}

 \section{SELECTED PATENTS}
   \begin{itemize}
    \item Capillary barriers for staged loading of microfluidic devices (2018), US10787660B2. US.  
    \item Systems, devices, and methods for isotachophoresis (2018), US11041150B2. US.
    \item Isotachophoresis for purification of nucleic acids, (2018), US201662288930P. US. 
   \end{itemize}


 \section{OPEN SOURCE}
   \begin{itemize}
     \item \textbf{Ionize} github.com/lewisamarshall/ionize\\
   An object oriented Python library for calculating the properties of
   aqueous solutions, including corrections for temperature, ionic strength, and ion-ion interactions.
 \end{itemize}


 \section{SKILLS}
   \begin{itemize}
     \item \textbf{Project Management}	Lead projects transparently with Gantt charts through a PDP.
 %     \item \textbf{Hiring}	Experienced leading hiring committees using transparent, modern hiring practices.
     \item \textbf{Programming}	Fluent in Python. Experienced managing contractors and in-house programmers. 
     \item \textbf{CAD Hardware Design} Experience designing parts in CAD, especially for injection molding. 
     \item \textbf{Electrical Design} Skilled reading electrical diagrams, and creating block diagrams for collaborative design. Experience designing simple PCBs for engineering setups. 
    %  \item \textbf{Machine Tools} Hobby-level machinist skills inform my designs and allow rapid iterations.

   \end{itemize}


%  \section{OTHER INTERESTS}
%    \begin{itemize}
%      \item \textbf{Woodworking}	I use hand tools and traditional techniques to make American vernacular furniture.
%      \item \textbf{Photography}	My use of scientific imaging led me to explore artistic photography.
%    \end{itemize}


\end{resume}
\end{document}
