% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage[T1]{fontenc}
\usepackage{kpfonts,baskervald}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page

\begin{document}

\name{Lewis A. Marshall\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name

\address{\bf  Address\\237 Ayrshire Farm Ln. \\ Apt. 103\\Stanford, CA 94305\\(650) 391-8463}

\address{\bf  Citizenship\\United States \\ \\ \bf E-Mail \\ lewis.a.marshall@gmail.com}

\begin{resume}

\section{JOB OBJECTIVE}
    A postdoctoral or comparable research position developing microfluidic devices and techniques, with emphasis on electrokinetics and capillary phenomena.

\section{EDUCATION}
		Stanford University, 2008--2013 \\
  		Ph.D., Chemical Engineering\\
  		Advisor: Juan G. Santiago\\  		

		University of Minnesota, 2004--2008 \\
  		B.S., Chemical Engineering\\


\section{EXPERIENCE}
   \vspace{-0.1in}

   \begin{tabbing}
   \hspace{2.1in}\= \hspace{2.9in}\= \kill % set up two tab positions
    {\bf Design Engineer} \>Purigen Biosystems  \>July~2013-Present\\
                             \>Sunnyvale, CA
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Working to commercialize a nucleic acid extraction technique. Designs and tests microfluidic chips for nucleic acid purification.

   \begin{tabbing}
   \hspace{2.1in}\= \hspace{2.9in}\= \kill % set up two tab positions
    {\bf Graduate Researcher} \>Stanford Microfluidic Laboratory    \>2009-Present\\
                             \>Stanford, CA
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Developed microfluidic devices and techniques for purification of nucleic acids from blood and other biological fluids using electrophoretic techniques. Performed molecular biological assays for nucleic acid analysis. Performed extensive microscopy and image analysis, including particle image velocimetry (PIV). Designed and fabricated PDMS and polystyrene microfluidic devices.
   \begin{tabbing}

   \hspace{2.1in}\= \hspace{2.9in}\= \kill % set up two tab positions
    {\bf Intern} \>Metropolitan Council Wastewater Treatment \>  Summer 2008\\
                          \>St. Paul, MN
   \end{tabbing}\vspace{-20pt}
    Analyzed centrate for foaming and settling of grit. Developed recommendations for improving centrifugation performance.
   \begin{tabbing}%
   \hspace{2.1in}\= \hspace{2.9in}\= \kill % set up two tab positions
   {\bf Undergraduate Researcher}  \>Hu Group, University of Minnesota \>   2005-2007\\
                          \>Minneapolis, MN
   \end{tabbing}\vspace{-20pt}
    Culture of CHO cells, microarray fabrication. Extensive use of polymerase chain reaction (PCR).


 \section{COMPUTER SKILLS}
 	\subsection{Programming}
 	Matlab for matrix programming.\\
 	R for figure generation.\\
 	Python for general programming.\\
 	For examples, please see www.github.com/lewisamarshall
 	\subsection{CAD}
 	Used Autocad and Draftsight to make 2D mask designs and general schematics.\\
 	Used AutoDesk Inventor to design chips for both 3D printing and injection molding,
 	as well as to generate 2D drawings for machining based on 3D models.


% \section{HONORS AND AWARDS}
%     Epsilon Delta Sigma: Honorary Management Society at
%     Rensselaer    \\
%     Dean's List of Distinguished Students: Fall 1986-Spring 1988  \\
%     National Honor Society: Northern Highlands High School  \\
%     Creative Essay Award: Northern Highlands High School  \\
%     Meritorious Action Life Saving Award: Boy Scouts of America

 \section{EXTRACURRICULAR ACTIVITIES}
     Officer, Atheists, Humanists, and Agnostics @ Stanford, 2009-2011\\
     Staff Writer, Stanford Static, 2012\\

\end{resume}
\end{document}
